Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-31 writeups/dissertation/dissertation.tex
foo

@@

The best-fit decay rate values were also analyzed across all dataset slices.
Aggregate best-fit decay rates were computed by taking the median of all user's best-fit decay rate value across all dataset slices.
The median was used since there were users in the popular-users dataset that did not have enough observations to generate stable predictions, and best-fit decay rate values for these users could be as high as 20.
Using the median effectively trims these unstable values from the sample, without having to define a cut point and go through an outlier removal process.

@@

That said, comparing the effect size between changing the decay rate value and using the standard form,
model accuracy improves much more when the standard form replaces the optimized learning form than when the decay rate value is increased from 0.5 to 0.8.
For these datasets, it is much more important to use the standard form of the equation than it is to adjust the decay rate, although model accuracy does slightly improve if a higher decay rate is chosen with the standard form.

>>>>

The best-fit decay rate values were analyzed across all dataset slices.
Aggregate best-fit decay rates were computed by taking the median of all user's best-fit decay rate values across all dataset slices.
The median was used since there were users in the popular-users dataset that did not have enough observations to generate stable predictions, and best-fit decay rate values for these users could be as high as 20.
Using the median effectively trims these unstable values from the sample, without having to define a cut point for an outlier removal process.

@@

ACT-R sets the default decay rate value to 0.5, and the best-fit value for the standard form is higher (0.8) for these datasets.
The figure shows that although model accuracy does improve for the standard form when increasing the decay rate parameter from 0.5 to the optimal value,
that percentage improvement is not as large as the improvement gained from using the standard form compared to the optimized learning form.
Nonetheless, model accuracy is highest when both the standard form is used and the decay rate value is increased.

@@
